3-advanced

### 2022-07-09 4-other-features.Rmd
use library("foo") style as suggested by JSS
use "e.g.," instead of "e.g."

Spatial locations can have grouping structures either inherent to the data (e.g. state within country) or obtained during the analysis (e.g. cluster id). In this case, it can be useful to summarize variables at various levels of the hierarchy. The function \code{switch_key()} can be used to change the grouping level of spatial locations. The diagram in Figure \ref{fig:illu-hier} shows how this function can be used to switch the grouping from station ids to cluster ids. The result can also be stretched into long form. By specifying

@@

The cubble workflow fits works well with an interactive graphics pipeline (e.g. @buja1988elements, @buja1996interactive,  @sutherland2000orca, @xie2014reactive, @cheng2016enabling) that is available in R with the package crosstalk [@crosstalk]. Figure \ref{fig:illu-interactive} illustrates how linking can be achieved between a map and multiple time series using a cubble. The map (produced from the nested form) and time series (produced from the long form) are both shared crosstalk objects. When a user makes a selection on the map, the site is highlighted (a). This activates a row in the nested cubble object, which is then communicated to the long cubble -- all the observations with the same \code{id} (b) will be selected. The long cubble will then highlight the corresponding series in the time series plot (c).

@@

```{r eval = FALSE, echo = TRUE}
library(ggplot2)
gly <- glyphs(data,
              x_major = ..., x_minor = ...,
              y_major = ..., y_minor = ..., ...)

>>>>

Spatial locations can have grouping structures either inherent to the data (e.g., state within country) or obtained during the analysis (e.g., cluster id). In this case, it can be useful to summarize variables at various levels of the hierarchy. The function \code{switch_key()} can be used to change the grouping level of spatial locations. The diagram in Figure \ref{fig:illu-hier} shows how this function can be used to switch the grouping from station ids to cluster ids. The result can also be stretched into long form. By specifying

@@

The cubble workflow fits works well with an interactive graphics pipeline (e.g., @buja1988elements, @buja1996interactive,  @sutherland2000orca, @xie2014reactive, @cheng2016enabling) that is available in R with the package crosstalk [@crosstalk]. Figure \ref{fig:illu-interactive} illustrates how linking can be achieved between a map and multiple time series using a cubble. The map (produced from the nested form) and time series (produced from the long form) are both shared crosstalk objects. When a user makes a selection on the map, the site is highlighted (a). This activates a row in the nested cubble object, which is then communicated to the long cubble -- all the observations with the same \code{id} (b) will be selected. The long cubble will then highlight the corresponding series in the time series plot (c).

@@

```{r eval = FALSE, echo = TRUE}
library("ggplot2")
gly <- glyphs(data,
              x_major = ..., x_minor = ...,
              y_major = ..., y_minor = ..., ...)
